\documentclass[11pt]{article}

\usepackage{jcd-macros}
\usepackage[numbers,square]{natbib}
\bluehyperref  % Dark blue hyperref
\usemedgeometry  % Use medium geometry (3cm left/right margin, 2.54 top/bottom)

\begin{document}

\title{26-05 Diagnosing and Correcting HDBSCAN Mergers for Latent-Mean
  Recovery Under a Gaussian-Mixture-Plus-Clutter Model}

\maketitle

\section{Some minor notes on discussion}

\paragraph{Responsible Parties:} Lucas (main), Ramesh, Tselil (on bullshit)

\begin{enumerate}[1.]
\item Much of this had a discussion on what was actually important: whether
  we needed to more communicate failure modes or whether we needed to
  actually provide procedures
\item Mike suggested maybe a checklist might be a very good idea
\item It may be interesting to link to some of Rong Ma's work on the failure
  of clustering (or the sensitivity of clustering procedures) to various
  idiosyncrasies in the data.
  %
  I (John) don't have the references off the top of my head right now.
\item Tselil had a nice dichotomy: you can educate people but you can never
  stop their bullshit (??)
\item Frankfurter's essay~\cite{Frankfurt86}
\end{enumerate}

\section{Lucas' contribution}
My proposal was just to fit maximum likelihood via the Expectation-Maximization algorithm, which is standard for mixture of Gaussians and should be trivial to extend to include one uniform component. EM requires an initialization and a number of clusters $N$; I propose searching over a range of $N$, and for each $N$ value initializing the cluster memberships via k-means, and using within-cluster sample mean and covariances to initialize the $A_i$ and $\Sigma_i$ parameters (possibly with some small amount of ridge regularization on $\Sigma$ if a cluster size is too small). Then run EM to get a final clustering and estimate of all parameters, and plug those parameters in to the mixture likelihood to compute a log likelihood score for that $N$. Make an elbow plot of the scores across $N$ values, looking for an elbow to choose a good value of $N$ (if none is apparently in the initial $N$ range tried, consider extending its range). 

The output of this algorithm allows for nice visualizations with ellipses for each cluster so the user can get a sense of which clusters lie where. If the output of HDBSCAN assigns clusters that are quite different from EM, then that could be a red flag. Alternatively, one could run this entire diagnostic separately on each individual cluster found by HDBSCAN, seeing whether EM splits any cluster into multiple clusters.

\bibliography{jcd-bib}
\bibliographystyle{abbrvnat}


\end{document}
