\documentclass[11pt]{article}

\usepackage{jcd-macros}
\usepackage[numbers,square]{natbib}
\bluehyperref  % Dark blue hyperref
\usemedgeometry  % Use medium geometry (3cm left/right margin, 2.54 top/bottom)

\begin{document}

\title{26-09 Dynamic Graph Clustering Revisited}

\maketitle

\section{Some minor notes on discussion}

\paragraph{Responsible Parties:} John (primary), Tselil/Lucas

\begin{enumerate}[1.]
\item Most agreed that modern literature was pretty rough on this one
\item Basic idea that many of us seemed to drill down on: building a running
  estimate of an adjacency matrix $A(t)$ could be an interesting
  procedure.
  %
  Then treat the clustering at time $t$ as the result of clustering on $A(t)$.
  %
  A few ways to do this:
  \begin{enumerate}[a.]
  \item Put down a statistical model of $A(t)$.
    %
    For example, a Poisson process on edges, and assume that the rate
    of the Poisson at time $t$ on edge $(i, j)$ is something like
    $\lambda_{ij}(t) = \theta_{ij}^T \phi(t)$, where $\phi(t)$ is a feature
    function of time.
    %
    Then fit this.
    %
    Note that this only works retrospectively (i.e., in filtering), and
    potentially nowcasting.
  \item A slightly less model-based way: constantly have a matrix
    $A(t)$ that, on each observation $(i, j, t)$, re-weights edge
    $(i ,j)$ according to some exponential (?) weighting.
  \end{enumerate}
\item A less model-based way: build a clustering.
  %
  As time goes on, keep a testing to see if the clustering satisfies a
  particular ``good enough'' criterion.
  %
  Upon failure of this criterion, re-estimate the clustering based on the
  observations since the last time the clustering worked.
\end{enumerate}

\section{Lucas' contribution}
I basically thought that the approach suggested near the end of the problem statement of using a time-weighted adjacency matrix at each time point (to which a non-dynamic clustering algorithm is applied) was a good class of procedures, where the choice of clustering algorithm and the choice of time weighting function are up to the user and should depend on the specifics of the problem (which we are not privy to). To me this is the most natural extension of standard state-of-the-art non-model-based clustering algorithms to the dynamic setting, since it basically takes a heuristic/non-model-based approach to smoothly linking things across time, and it seems like if one does that well, I'm not sure how one could do anything much better unless there's a lot of strong modeling and/or domain knowledge about the problem (which, even if there were, we wouldn't really be able to advise on using since the NSA wouldn't share it with us).

\end{document}
