\documentclass[11pt]{article}

\usepackage{jcd-macros}
\usepackage[numbers,square]{natbib}
\bluehyperref  % Dark blue hyperref
\usemedgeometry  % Use medium geometry (3cm left/right margin, 2.54 top/bottom)

\begin{document}

\title{26-10 Intermittent Sparse Signals Associated with Events}

\maketitle

\section{Some minor notes on discussion}

\paragraph{Responsible Parties:} Lucas, John

\begin{enumerate}[1.]
\item Basic model: there's a Taylor swift concert in one of some number
  $K$ of cities.
  %
  The matrix $X \in \R^{n \times p}$ represents traffic at the $n$ timesteps
  preceding the concert, which (say) has $X_{ij} \simiid \poisson(\lambda_j)$.
  %
  Then $\tau$ timesteps preceding the concert, the roads into the
  arena in town $k$ start to increase, so there's an index set
  $I_k \subset [p]$, with $|I_k| \ll p$, and on those
  $X_{ij} \simiid \poisson(\lambda_j + \theta_j)$ for $j \ge n - \tau$.
\item Lucas's basic idea: what about writing down some empirical Bayes
  models for this?
\item The proposer wants to know methods on this one, \emph{not} too fussed
  about the theory of it.
\end{enumerate}

\section{Lucas' contribution}
It seems like an empirical Bayes approach would be a robust and efficient way to share strength across events. A few questions arise:
\begin{itemize}
    \item how to initialize the estimates of the hyperparameters? I also have to think more on this, since it usually depends on the specific model.
    \item how to do the Bayesian inference for $I_k$, which is a sparse recovery problem in high dimensions, which Bayesian sampling methods don't tend to scale well to? eems like there should be a way to plug in something frequentist that scales much better, but I have to think more on this.
\end{itemize}

\end{document}
